On the specific recursive structure of iterated parametricity

### 2025-10-26 paper/paper.tex
paper: restrl is complex

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][0,...,p]    &                                              & :      & Type_{l+1}                                                                                       \\
    \frametype[n][]           &                                              & \defeq & \unittype                                                                                        \\
    \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n+1][0,...,p-1] \times Type_l                                                         \\
    \\
    \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & Type_{l+1}                                                                                       \\
    \paintingtype[n][]        & \unitpoint                                   & \defeq & \unittype                                                                                        \\
    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
    \layertype[n][p]          & \framep[n][p]                                & :      & Type_{l+1}                                                                                       \\
  \end{array}
\end{equation*}

Formally, this can be described as:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \framep[n][0,...,p]           &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
                \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
                \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                \left(\begin{array}{l}
                    \framep[n][0,...,p-1]   \\
                    \painting[n][0,...,p-1] \\
                  \end{array}\right)                                              \\
              \end{array}\right) : \frametype[n][0,...,p]
    }                                                                  \\
    \framep[n][0]                 &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)        & \defeq & (\unitpoint,unit)       \\
    \framep[n][0,...,p+1]         &
    \left(\begin{array}{l}
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
              \restrf[n][0,...,p]   \\
            \end{array}\right)      & \defeq &
    \left(\begin{array}{l}
              \framep[n+1][0,...,p]
              \left(\begin{array}{l}
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right), \\
              \Sigma d:\framep[n+1][0,...,p]
              \left(\begin{array}{l}
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right).\, \\
              \quad \layer[n][p]
              \left(\begin{array}{l}
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right) \\
            \end{array}\right)                   \\
    \restrftype[n][0,...,p-1]     &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
                \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
              \end{array}\right) : Type_{l}
    }                                                                  \\
    \restrftype[n][0,...,0-1]     &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)        & \defeq &
    \unittype                                                          \\
    \restrftype[n][0,...,(p+1)-1] &
    \left(\begin{array}{l}
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
            \end{array}\right)      & \defeq &
    \begin{array}{l}
      \Sigma \restrf[n+1][0,...,p-1]
      :\restrftype[n+1][0,...,p-1]
      \left(\begin{array}{l}
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
              \end{array}\right).                     \\
      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
      \left(\begin{array}{l}
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
                \restrf[n+1][0,...,p-1]   \\
              \end{array}\right) \rightarrow  \framep[n][p] \\
    \end{array} \\
    \layer[n][p]                  &
    \left(\begin{array}{l}
              \framep[n][0,...,p]     \\
              \painting[n][0,...,p]   \\
              \restrf[n+1][0,...,p-1] \\
            \end{array}\right)    & \defeq &
    \Pi\omega.\,\painting[n][p](\restrf[n][p](d))
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][p,...,n]         &                                              & :         & Type_{l+1}                                                                                   \\
    \frametype[n][]                &                                              & \defeq    & \unittype                                                                                    \\
    \frametype[n][p,...,n]         &                                              & \defeq    & Type_l \times \frametype[n][p+1,...,n-1]                                                     \\
    \\
    \paintingtype[n][p,...,n]      & (\framep[n][p,...,n]:\frametype[n][p,...,n]) & :         & Type_{l+1}                                                                                   \\
    \paintingtype[n][]             & \unitpoint                                   & \defeq    & \unittype                                                                                    \\
    \paintingtype[n][p,...,n](p<n) & (\framep[n][p,...,n])                        & \defeq    & (\framep[n][p] \rightarrow Type_l) \times \paintingtype[n][p+1,...,n](\framep[n][p+1,...,n]) \\
    \\
    \restrftype[n][p,...,n]        &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \deps[n-1][0,...,p-1]:\depstype[n-1][0,...,p-1]                                  \\
                \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
                \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
              \end{array}\right) : Type_{l}
    }                                                                                                                                                                                        \\
    \restrftype[n][]               &
    \left(\begin{array}{l}
              \deps[n-1][0,...,n-1] \\
              \unitpoint            \\
              \unitpoint            \\
            \end{array}\right)       & \defeq                                       & \unittype                                                                                                \\
    \restrftype[n][p,...,n-1]      &
    \left(\begin{array}{l}
              \deps[n-1][0,...,p-1]     \\
              \framep[n-1][p,...,n-1]   \\
              \painting[n-1][p,...,n-1] \\
            \end{array}\right)
                                   & \defeq                                       &
    \begin{array}{c}
      \framep[n][p]
      \left(\begin{array}{l}
                \deps[n-1][0,...,p-1] \\
              \end{array}\right)
      \rightarrow \framep[n-1][p] \\
      \times                      \\
      \restrftype[n][p+1,...,n]
      \left(\begin{array}{l}
                \deps[n-1][0,...,p]         \\
                \framep[n-1][p+1,...,n-1]   \\
                \painting[n-1][p+1,...,n-1] \\
              \end{array}\right)
    \end{array}
  \end{array}
\end{equation*}

This allows to define $\painting[n][p]$ formally:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n][p]          &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \deps[n-1][0,...,n-1]:\depstype[n-1][0,...,n-1] \\
                E:\framep[n-1][n-1]\rightarrow Type_l           \\
              \end{array}\right) : \framep[n-1][n-1]\rightarrow Type_l
    }                                                            \\
    \painting[n][n]          &
    \left(\begin{array}{l}
              \deps[n-1][0,...,n-1] \\
              E                     \\
            \end{array}\right) & \defeq & E                        \\
    \painting[n][p](p<n)     &
    \left(\begin{array}{l}
              \deps[n-1][0,...,n-1] \\
              E                     \\
            \end{array}\right) & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer(\deps[n-1][0,...,p-1]). \\
              \painting[n][p+1,...,n-1]
              \left(\begin{array}{l}
                  \deps[n-1][0,...,n-1] \\
                  E                     \\
                \end{array}\right)(d,l)           \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

to do : def of restrptype

Mutual definition of \restrf and cohframetype

@@

              \end{array}\right) : \restrftype[n][0,...,p]

@@

      \lambda q.\lambda \epsilon.\lambda (\framep[n+1][0,...,p], \layer[n][p]). \\

@@

@@

@@

              \end{array}\right) : Type_{l}

@@

@@

              \deps[n][0,...,n]:\depstype[n][0,...,p] \\
              \layer[n+1][p]:\layertype[n+1][p]       \\

@@

    \restrltype[n][p]                                                                                                      \\

@@

              \layer[n][p]      \\

@@

    \lambda\omega.\,\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega]}{\restrp[n][p](\layer[n][p])}                      \\

@@

Definition of \cohf, using $\UIP$ to solve the dependency in $\coht$.

>>>>

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][0,...,p]    &                                              & :      & \U                                                                                           \\
    \frametype[n][]           &                                              & \defeq & \unittype                                                                                    \\
    \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n+1][0,...,p-1] \times \U                                                         \\
    \\
    \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & \U                                                                                           \\
    \paintingtype[n][]        & \unitpoint                                   & \defeq & \unittype                                                                                    \\
    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow \U) \\
  \end{array}
\end{equation*}

Formally, this can be described as:
    \framep[n][0,...,p]                                  &
                \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
                \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
                \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                    \framep[n][0,...,p-1]   \\
                    \painting[n][0,...,p-1] \\
              \end{array}\right) : \frametype[n][0,...,p]
    \framep[n][0]                                        &
            \end{array}\right)                               & \defeq                                       & (\unitpoint,unit)            \\
    \framep[n][0,...,p+1]                                &
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
              \restrf[n][0,...,p]   \\
              \framep[n+1][0,...,p]
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
              \Sigma d:\framep[n+1][0,...,p]
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right).\, \\
              \quad \layer[n][p]
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right)(d) \\
    \restrftype[n][0,...,p-1]                            &
              \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
              \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
            \end{array}\right) : \U
    \restrftype[n][0,...,0-1]                            &
    \restrftype[n][0,...,(p+1)-1]                        &
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
      \Sigma \restrf[n+1][0,...,p-1]
      :\restrftype[n+1][0,...,p-1]
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
                \restrf[n+1][0,...,p-1]   \\
              \end{array}\right) \rightarrow  \framep[n][p] \\
    \layertype[n][p]                                     & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & : \framep[n][p] \rightarrow \U \\
    \layer[n][p]                                         &
              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
              \restrf[n+1][0,...,p-1]:\restrftype[n][0,...,p-1] \\
    d \mapsto \Pi\omega.\,\painting[n][p](\restrf[n][p](d))

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][p,...,n]         &                                              & :         & \U                                                                                       \\
    \frametype[n][]                &                                              & \defeq    & \unittype                                                                                \\
    \frametype[n][p,...,n]         &                                              & \defeq    & \U \times \frametype[n][p+1,...,n-1]                                                     \\
    \\
    \paintingtype[n][p,...,n]      & (\framep[n][p,...,n]:\frametype[n][p,...,n]) & :         & \U                                                                                       \\
    \paintingtype[n][]             & \unitpoint                                   & \defeq    & \unittype                                                                                \\
    \paintingtype[n][p,...,n](p<n) & (\framep[n][p,...,n])                        & \defeq    & (\framep[n][p] \rightarrow \U) \times \paintingtype[n][p+1,...,n](\framep[n][p+1,...,n]) \\
    \\
    \restrftype[n][p,...,n]        &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
              \deps[n-1][0,...,p-1]:\depstype[n-1][0,...,p-1]                                  \\
              \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
              \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
            \end{array}\right) : \U
    }                                                                                                                                                                                    \\
    \restrftype[n][]               &
    \left(\begin{array}{l}
              \deps[n-1][0,...,n-1] \\
              \unitpoint            \\
              \unitpoint            \\
            \end{array}\right)       & \defeq                                       & \unittype                                                                                            \\
    \restrftype[n][p,...,n-1]      &
    \left(\begin{array}{l}
              \deps[n-1][0,...,p-1]     \\
              \framep[n-1][p,...,n-1]   \\
              \painting[n-1][p,...,n-1] \\
            \end{array}\right)
                                   & \defeq                                       &
    \begin{array}{c}
      \framep[n][p]
      \left(\begin{array}{l}
                \deps[n-1][0,...,p-1] \\
              \end{array}\right)
      \rightarrow \framep[n-1][p] \\
      \times                      \\
      \restrftype[n][p+1,...,n]
      \left(\begin{array}{l}
                \deps[n-1][0,...,p]         \\
                \framep[n-1][p+1,...,n-1]   \\
                \painting[n-1][p+1,...,n-1] \\
              \end{array}\right)
    \end{array}
  \end{array}
\end{equation*}

This allows to define $\painting[n][p]$ formally:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n][p]          &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \deps[n-1][0,...,n-1]:\depstype[n-1][0,...,n-1] \\
                E:\framep[n-1][n-1]\rightarrow \U               \\
              \end{array}\right) : \framep[n-1][n-1]\rightarrow \U
    }                                                            \\
    \painting[n][n]          &
    \left(\begin{array}{l}
              \deps[n-1][0,...,n-1] \\
              E                     \\
            \end{array}\right) & \defeq & E                        \\
    \painting[n][p](p<n)     &
    \left(\begin{array}{l}
              \deps[n-1][0,...,n-1] \\
              E                     \\
            \end{array}\right) & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer(\deps[n-1][0,...,p-1]). \\
              \painting[n][p+1,...,n-1]
              \left(\begin{array}{l}
                  \deps[n-1][0,...,n-1] \\
                  E                     \\
                \end{array}\right)(d,l)           \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

At this stage, we are able to define $\framep$, $\painting$ and $\restrftype$ from $\deps$ at the previous level. To go further, we need to define the sequence $\restrptype$ of types of painting restrictions:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrptype[n][0,...,p] & (\deps[n][0,...,n]:\depstype[n][0,...,n]) & :      & \U                                        \\
    \restrptype[n][]        & \unitpoint                                & \defeq & \unittype                                 \\
    \restrptype[n][0,...,p] & (\deps[n][0,...,n])                       & \defeq & \restrptype[n+1][0,...,p-1] \times \left(
    \begin{array}{l}
        \deps[n+1][0,...,p-1].                            \\ \Pi q\leq n.\Pi \epsilon.\Pi d:\framep(\deps).\\
        \painting[n][p](\deps[n][0,...,n])(d) \rightarrow \\ \deps.\painting[n][p](\deps.\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                                                  \\
  \end{array}
\end{equation*}

Mutual definition of $\restrf$ and $\cohftype$

@@

              \end{array}\right) :
      \restrftype[n][0,...,p]
                \deps.\frame[n][0,...,p]    \\
                \deps.\painting[n][0,...,p] \\
              \end{array}\right)

@@

              \lambda q.\lambda \epsilon.\lambda (d,l]). \\

@@

                  \end{array}\right)(d), \restrl[n][p]

@@

                  \end{array}\right)(d)(l)\right)      \\
            \end{array} \right)                                                            \\

@@

            \end{array}\right) : \U

@@

    \restrltype[n][p]                          &
            \end{array}\right)
                                               & :      & \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n][p].\left(
        \layer[n][p]\left(
            \framep[n][p](\deps[n][0,...,p])   \\
            \painting[n][p](\deps[n][0,...,n]) \\
            \restrf[n][p](\deps[n][0,...,p])   \\
          \end{array}\right)(d) \rightarrow \\
        \layer[n][p](\deps[n][0,...,n])(\restrf[n][p](d))

@@

@@

    \restrltype[n][p] \left(\begin{array}{l}
    \right)                                                                                                                \\

@@

@@

    \lambda\omega.\,\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega]}{\restrp[n][p](l \omega)}                          \\

@@

Definition of $\cohf[n][p]$, using $\UIP$ to solve the dependency in $\coht[n][p]$.
